MSB1015 Project

### 2024-10-18 Code/MSB1015-Project.Rmd
Update MSB1015-Project.Rmd
Added visualisation before and after imputation

# Load the data
data <- read_csv("METABRIC_RNA_Mutation.csv")
```

@@

@@

# Select only the transcription data
pca_gx <- data_filled %>%
  select(brca1:ugt2b7)

# Perform PCA to check the columns with the highest amount of missing values
pca <- prcomp(pca_gx, center = TRUE, scale. = TRUE)

# Convert PCA results to data frame
pca_data <- as.data.frame(pca$x[, 1:3])
pca_data$tumor_stage <- as.factor(data_filled$tumor_stage)

# Create pairwise plots using ggpairs
ggpairs(pca_data,
  mapping = aes(color = tumor_stage),
  upper = list(continuous = wrap("points")),
  lower = list(continuous = wrap("points")),
  diag = list(continuous = wrap("barDiag"))
) +
  theme_minimal()
```

@@

@@

# Load the function for PCA
source("~/University/MSB/MSB1015/funPCA.R") # Change the directory as needed

# Call the function for the unsupervised random forest PCA
pca_plots_categorical <- pca_proximity_plot(categorical_data, "prognosis")
grid.arrange(grobs = pca_plots_categorical, ncol = 2)

@@

# Call the function for the unsupervised random forest PCA (will take a few minutes)
pca_plots_genetic <- pca_proximity_plot(genetic_data, "prognosis")
grid.arrange(grobs = pca_plots_genetic, ncol = 2)

@@

# Call the function for the unsupervised random forest PCA (will take a few minutes)
pca_plots_complete <- pca_proximity_plot(complete_data, "prognosis")
grid.arrange(grobs = pca_plots_complete, ncol = 2)
```

@@

# Call the plotting function for the confusion matrix
source("~/University/MSB/MSB1015/confusionPlot.R") # Load external plot function (update directory if needed)
confusionPlot(train_confusion, title = "Confusion Matrix (Training Set)") # Plot confusion matrix

>>>>

# Load the function for PCoA
source("~/University/MSB/MSB1015/funPCoA.R") # Change the directory as needed

# Load the confusion function
source("~/University/MSB/MSB1015/confusionPlot.R")

# Load the data
data <- read_csv("METABRIC_RNA_Mutation.csv")

@@

# Call the function for the unsupervised random forest PCA
PCoA_plots_rawdata <- PCoA_proximity_plot(data, "tumor_stage")
grid.arrange(grobs = PCoA_plots_rawdata, ncol = 2)

@@

@@

# Call the function for the unsupervised random forest PCoA 
PCoA_plots_rawdata <- PCoA_proximity_plot(data, "tumor_stage", n_trees = 10)
grid.arrange(grobs = PCoA_plots_rawdata, ncol = 2)

@@

# Call the function for the unsupervised random forest PCoA
PCoA_plots_categorical <- PCoA_proximity_plot(categorical_data, "prognosis")
grid.arrange(grobs = PCoA_plots_categorical, ncol = 2)

@@

# Call the function for the unsupervised random forest PCoA (will take a few minutes)
PCoA_plots_genetic <- PCoA_proximity_plot(genetic_data, "prognosis")
grid.arrange(grobs = PCoA_plots_genetic, ncol = 2)

@@

# Call the function for the unsupervised random forest PCoA (will take a few minutes)
PCoA_plots_complete <- PCoA_proximity_plot(complete_data, "prognosis")
grid.arrange(grobs = PCoA_plots_complete, ncol = 2)
```

@@

# Call the plotting function for the confusion matrix
confusionPlot(train_confusion, title = "Confusion Matrix (Training Set)") # Plot confusion matrix
